Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-06-24 kappa.tex
Add atmospheric forcing subsection.

>>>>

Atmospheric forcing of the model consists of a present-day monthly climatology,
$\{T_{m0}, P_{m0}\}$, modified by a lapse-rate correction, ${\Delta}T_{LR}$,
and a temperature-offset correction, ${\Delta}T_{TS}$,
\begin{align}
    T_m(t, x, y) &= T_{m0}(x, y) +{\Delta}T_{LR}(t) +{\Delta}T_{TS}(t, x, y),\\
    P_m(t, x, y) &= P_{m0}(x, y).
\end{align}

The present-day climatology, $\{T_{m0}, P_{m0}\}$, is computed from
near-surface air temperature and precipitation rate fields extracted from
observational data and atmospheric reanalyses.
The lapse-rate correction, ${\Delta}T_{LR}$, is computed in relation to the
climate input reference bedrock topography, $b_{ref}$,
\begin{align}
    {\Delta}T_{LR}(t, x, y) &= -\gamma [s(t, x, y)-b_{ref}(x, y)] \\
                            &= -\gamma [h(t, x, y)+b(t, x, y)-b_{ref}(x, y)],
\end{align}

thus accounting for the evolution of ice thickness, $h$, on the one hand, and
for differences between the the ice flow model basal topography, $b$, and the
climate input topography, $b_{ref}$, on the other hand. All simulations use an
annual temperature lapse rate of $\gamma = 6\,\unit{\degC\,km^{-1}}$.

Paper~I tests the sensitivity of the model to different input present-day
climatologies, $\{T_{m0}, P_{m0}\}$, while the temperature-offset corrections,
${\Delta}T_{TS}$, uses constant values ranging from -10 to 0\,\degC. Paper~IV,
on the opposite, tests model sensitivity to time-dependent temperature-offset
corrections derived from different palaeo-temperature proxy records.
